Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-05 paper/flairs27/content/results.tex
Some table moving arounds

\begin{table}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

\begin{tabular}{|c|l|}
\hline 
\textbf{\# of Documents} & \textbf{Document Type}\\ 
\hline 
10988 & 	arxiv  \\ \hline
34887 & Classified \\ \hline
77674 & Forum  \\ \hline
12947 & Linking  \\ \hline
141936 & Mainstream News  \\ \hline
4137 & Memetracker \\ \hline
280629 & News \\ \hline
6347 &  Review \\ \hline
688848 & 	 Social  \\ \hline
740987 & Weblog \\ \hline

@@

We have 135 extraction patterns coverin each slot-name/entity-type combinations. Our final submission was named \textit{submission\_infer}. Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference. Slot extraction using patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.

@@

\begin{table}[htp]
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}

>>>>

\begin{table}[b]
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

\begin{tabular}{|l|c|c|}
\hline 
\textbf{\# of Documents} & \textbf{Document Type} & \textbf{Slots Found}\\ 
\hline 
	Arxiv & 10988 & \\ \hline
 Classified & 34887 & \\ \hline
 Forum & 77674 & \\ \hline
 Linking & 12947 & \\ \hline
 Mainstream News & 141936 & \\ \hline
 Memetracker & 4137 & \\ \hline
 News & 280629 & \\ \hline
 Review & 6347 & \\ \hline
 	 Social & 688848 & \\ \hline
 Weblog & 740987 & \\ \hline

@@

We have 135 extraction patterns covering each slot-name/entity-type combinations. Our final submission was named \textit{submission\_infer}. Our results are as follows: Document extraction using query entity matching with aliases, sentence extraction using alias matching and co-reference. Slot extraction using patterns, NER tags and NP tags. 158,052 documents with query entities, 17885 unique extracted slot values for 8 slots and 139 entities, 4 slots and 31 entities missing.

@@

\begin{table}
\caption{SSF Performance Measure on \textit{initial\_submission} }
\centering
\label{table:initialresult}
